An Overview of Distributed Version Control Systems

### 2010-07-04 laarsample.tex
Fusionadas las secciones Change-sets y Patchs

% Reveer diferencia entre changes & patch. Ver bien la diferencia o juntarlos.
%Arq
\subsection{Change-sets}
You could also create several other clones for every feature or bug that you want to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to your local clone. To be able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.

\subsection{Patchs}
The idea of having several clones, one for each feature or bug might be problematic. Instead, it is possible to have a single clone and then select
which of the local changes goes into the commit. Different parts of a single file can be selected to join the commit and which ones doesn't. Only those selected parts will conform the commit. The ability to select only parts of all the modifications makes the commits very atomic.

>>>>

\subsection{Change-sets}
It is very easy to create several other clones for every feature or bug that the developer wants to develop and push those changes to another clone, a peer's repository for instance, and pull some changes from another peer to the local clone. To be able to do this, a DVCS tracks change-sets instead of changes in individual files so that it can keep track of all the changes needed for a feature/bug to work.

To make better fine grain changesets, it is possible to select which of the developer's local changes goes into the commit.
Different parts of a single file can be selected to join the commit and which ones doesn't. 
Only those selected parts will conform the commit. The ability to select only parts of all the modifications makes the commits very atomic.
